
The measured data agreed with the
theory for all samples, and the $\chi^2$ statistic can be calculated

\begin{equation}
    \chi^2 = \sum_{i=1}^8 \dfrac{(R_{\text{obs}} -
    R_{\text{th}})^2}{\mathop{\mathrm{Var}}(R_{\text{obs}})} = 2.31.
    \label{eqn:chisq}
\end{equation}

With 7 degrees of freedom, this results in a right-tail probability of 0.94 that the 
observations are consistent with the model, thus validating the quantitative estimation of
dark-field values for a lung model as a collection of incoherently
superimposed microscopic spheres.

Possible sources of inaccuracy of our model include a significantly
different distribution of shapes in the lung parenchyma, or additional
effects of beam hardening which are known to influence the dark-field
signal. In order to consider the effects of possible shape asymmetries, a
single mouse lung sample was scanned at the X02DA TOMCAT beamline with the
setup described in Kagias et al.~\cite{PhysRevLett.116.093902}. This
technique is similar to Talbot interferometry, but it is able to detect
scattering from unresolved microscopic structures under different angles in
a single shot by
creating an array of circular interference patterns. The intensity of the
dark-field signals for different angles can then be recovered for each
pixel, and an asymmetry value defined as the amplitude of this periodic
signal divided by the average can be calculated for each pixel. This allows
us to exclude the possibility that there are significant inhomogeneities in
the dark-field response of the lung structures under different angles, which
would directly invalidate the model of a superposition of spheres. This
amounts to quantifying the departure from a spherical model towards
ellipsoids. In our sample this asymmetry is an average of $0.11 \pm 0.04$, indicating a departure from the spherical model of less than 15\%.

Another effect commonly reported in dark-field analyses on wide, polychromatic
sources is the influence of beam hardening on the recorded dark-field
values. In our case, given the high voltage of the source and the small
thickness of the samples (less than 4 mm), the absorption ranges from 4\% to
6\%. The correction to dark-field values provided by is therefore
not applied, as it is reported to be relevant for samples absorbing at least
50\% of the incoming light. The beam hardening effect is considered insofar
it affects the spectral weights of eq.~\ref{eqn:totalsum}, which are calculated
after the sample.

While this setup has a short autocorrelation length of only few micrometers
(figure~\ref{725462}), it would be possible to design a setup that is more
sensitive to the structure sizes found in human lungs, where the alveoli are
larger than
100 μm~\cite{Ochs_2004}. We can describe a
possible choice of parameters for a Talbot-Lau interferometer for lung
screening. The design energy can be chosen as \SI{60}{\kilo\eV}, close to
the mean voltage for a 100 kV setting on a chest
radiography. An intergrating length of 1 m is required to provide
enough room for the patient to comfortably fit the machine,
and a period of 1.2 μm could be achievable without
excessively stretching the requirements on the fabrication of the optical
elements. This results in an autocorrelation length around
\SI{25}μm, which is large enough to provide contrast according
to the mechanism shown in figure~\ref{725462}, thus providing better contrast than the
current setup.